---
title: "House Prices"
author: "Graham Parkes"
date: "18/06/2017"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

title 1
=======

title 2
-------


## House Prices: Predicting Sale Prices Based On Characteristics

This notebook explores the data set provided by kaggle [House Prices: Advanced Regression Techniques](https://www.kaggle.com/c/house-prices-advanced-regression-techniques).  The objective of this is to develop a model to predict sale prices based on the characteristics of each one.

The dataset was explored using the following libraries: readr, purrr, dplyr, plyr, Alelia, tidyr, ggplots, stringr, gbm,caret and forcats.

```{r echo=FALSE, message=FALSE}
library(readr)
library(purrr)
library(plyr)
library(dplyr)
library(Amelia)
library(tidyr)
library(ggplot2)
library(stringr)
library(gbm)
library(forcats)
library(caret)
```

The data was supplied as a CSV data set.

```{r echo=FALSE, message=FALSE}
house_raw <- read_csv('train.csv')
```

The data set contains details of `r nrow(house_raw)` properties with `r ncol(house_raw)-1` attributes.

Not every house has every attribute, and some require cleaning.
These items were not populated

```{r}
# check columns for na
check_na <- function(f) {sum(is.na(f))}


absent_data_cols <- summarise_all(house_raw,check_na)
absent_data_cols_ind <- absent_data_cols[1,]>0
absent_items <- t(absent_data_cols[,absent_data_cols_ind[1,]])
absent_items <- cbind(absent_items,feature=row.names(absent_items))
absent_items <- as.data.frame(absent_items,stringsAsFactors=FALSE) 
names(absent_items)[1] <- "gaps"
absent_items$gaps <- as.numeric(absent_items$gaps)
absent_items <- absent_items[order(absent_items$gaps,decreasing = TRUE),]
row.names(absent_items) <- NULL
absent_items %>% ggplot() + geom_col(aes(reorder(feature,order(absent_items$gaps,decreasing = TRUE)),gaps,fill=gaps)) + coord_flip() + labs(title="Potential Data Gaps",x="Feature")


```
```{r echo=FALSE}

```

